Prospective testing for the prevalence or transience of a shock effect over a set time horizon before it occurs

### 2022-03-12 prevalence_testing/postshocktest2021draft.tex
addition of statements related to weighted AIC

Note that the mean squared error of estimating $\P(p_1\leq \alpha)=\kappa_1$ is
\begin{align*}
	\E\bigg\{ \Big\{ \sum_{i\in \mc{I}_n} w_i I(p_i\leq \alpha)-\kappa_1 \Big\}^2 \bigg\}
	&= \Big\{ \sum_{i\in \mc{I}_n} w_i \kappa_i -\kappa_1 \Big\}^2 + \var 
	\Big\{\sum_{i\in \mc{I}_n} w_i I(p_i\leq \alpha) \Big\}\\
	&= \Big\{ \sum_{i\in \mc{I}_n} w_i \kappa_i -\kappa_1 \Big\}^2  + \sum_{i\in \mc{I}_n} w_i^2 \kappa_i (1-\kappa_i) \\
	& \overset{n\to \infty }{\to} \sum_{i\in \mc{I}_n} w_i^2 \kappa_i (1-\kappa_i) ,
\end{align*}
where the last second step assumes that $\{I(p_i\leq \alpha)\colon i\in \mc{I}_n\}$ are independent and the last step uses the condition $\sum_{i\in \mc{I}_n} w_i \kappa_i \to \kappa_1$ as $n\to \infty$, which is used in Corollary \ref{coro1}. Notice that if $\kappa_i$ is very small, the mean squared error of $\sum_{i\in \mc{I}_n} w_i I(p_i\leq \alpha)$ turns out to be small such that by the rationale of the proof of Proposition \ref{votprop}, the asymptotic approximation for the misclassification error in  Corollary \ref{coro1} should be acceptable.

>>>>

Note that the mean squared error of estimating $\P(p_1\leq \alpha)=\kappa_1$ is
\begin{align*}
	\E\bigg\{ \Big\{ \sum_{i\in \mc{I}_n} w_i I(p_i\leq \alpha)-\kappa_1 \Big\}^2 \bigg\}
	&= \Big\{ \sum_{i\in \mc{I}_n} w_i \kappa_i -\kappa_1 \Big\}^2 + \var 
	\Big\{\sum_{i\in \mc{I}_n} w_i I(p_i\leq \alpha) \Big\}\\
	&= \Big\{ \sum_{i\in \mc{I}_n} w_i \kappa_i -\kappa_1 \Big\}^2  + \sum_{i\in \mc{I}_n} w_i^2 \kappa_i (1-\kappa_i) \\
	& \overset{n\to \infty }{\to} \sum_{i\in \mc{I}_n} w_i^2 \kappa_i (1-\kappa_i) ,
\end{align*}
where the last second step assumes that $\{I(p_i\leq \alpha)\colon i\in \mc{I}_n\}$ are independent and the last step uses the condition $\sum_{i\in \mc{I}_n} w_i \kappa_i \to \kappa_1$ as $n\to \infty$, which is used in Corollary \ref{coro1}. Notice that if $\kappa_i$ is very small, the mean squared error of $\sum_{i\in \mc{I}_n} w_i I(p_i\leq \alpha)$ turns out to be small such that by the rationale of the proof of Proposition \ref{votprop}, the asymptotic approximation for the misclassification error in  Corollary \ref{coro1} should be acceptable.\\

Suppose we are interested in comparing two models $\mc{M}_1$ and $\mc{M}_2$ using AIC for forecasting the response in the time series of interest. However, direct comparison is not feasible as the data are not observed. Instead, we can conduct such inference based on the donor pool. Let the AIC of $\mc{M}_j$ for $i$th time series be $a_i^j$ for $i = 1, \ldots, n+1$ and $j = 1, 2$. Let $\xi_i = \P(a_i^1 > a_i^2)$. Note that if the data generating process is based on $\mc{M}_1$ and is true for all the donors and time series of interest, $\xi_i$ is expected to be high. Additionally, it is reasonable to assume $\xi_i =\xi $ for $\xi \in [0,1]$ and $i = 1, \ldots, n+1$.  Notice that this setup is similar to the setup of weighted voting or voting we discussed before. So, under similar arguments, we propose the following corollary for synthetic pairwise model selection.

\begin{corollary}[Synthetic pairwise model selection]
\label{coro1}Let $(w_2, \ldots, w_{n+1})$ be weights such that $w_i \in [0,1]$ and $\sum_{i=2}^{n+1} w_i=1$. Define
\begin{align*}
  \mc{I}_n = \{i =  2,\ldots, n+1\colon 0< w_i < 1\}.
\end{align*}
Suppose that  $\mc{I}_n$  is non-empty, $|\mc{I}_n| \to \infty$ as $n \to \infty$, and $w_i b_n\leq K$ for $i\in \mc{I}_n$ and some $K>0$, where $b_n \geq 1$ and $b_n \to \infty$ as $n\to \infty$. Assume for $i \in \mc{I}_n$,  $\{a_i^1, a_i^2\}$ are pairwise independent AICs of $\mc{M}_1$ and  $\mc{M}_2$ for $i$th time series  with 
\begin{align*}
  \sum_{i\in \mc{I}_n}\P(a_i^1 > a_i^2) = \sum_{i\in \mc{I}_n} w_i \xi_i \to \xi_{1},
\end{align*}
where $\xi_i =  \P(a_i^1 > a_i^2)\in [0,1]$ for $i \in \mc{I}_n$. If $\xi  \neq 0.5$, as $n\to \infty$, 
\begin{align*}
  \E \bigg\{\left|I\left\{ \sum_{i\in \mc{I}_n} w_i I(a_i^1 > a_i^2) \geq 0.5\right\}
  - I( a_1^1 > a_1^2) \right|\bigg\}
  \to  \begin{cases}
    1- \xi_1 & \text{ if } \xi_1 > 0.5 \\
   \xi_1 & \text{ if } \xi_1 < 0.5 
  \end{cases}
\end{align*}
\end{corollary}
